An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/eval.tex
config: eval

We conduct three parts of experiments to evaluate our \app
prototype. We want to answer several questions:

@@

\item Whether \app can detect real-world configuration errors?

\item How does the size of training dataset impact on the correctness
  of \app?

\item What is the rule inference accuracy?

\item How long can we run the verification?

@@

\subsection{Training Set Impact}

In this experiment, we vary the number of training configuration files,
and observe whether the correctness of \app would increase 
accordingly. \ennan{We may need a table whose x-axis is the number
of entries in the training configuration files, and y-axis is the 
accuracy or something close.}

>>>>

We conduct three experiments to evaluate our \app
prototype. Our experiments aim to answer the following
questions.

@@

\item Whether \app can successfully 
  detect real-world configuration errors?

\item Whether \app can correctly detect anomalous values?

\item How long do training and verification last?

@@

\subsection{Detecting Anomalous Values}

The purpose of checking anomalous values in configuration files 
is to avoid potential performance or workload problems. 
Checking anomalous values is mainly the responsibility of
the second sub-module checker of \app (see $\S$\ref{sec-checker}).

We run \app to check 30 real-world benchmarks from Stack Overflow 
website, and found \app is able to report anomalous values in
these configurations. We also manually check whether these
anomalous values are correct by comparing our results with
the answers on Stack Overflow.

Table~\ref{table-anomaly} shows three examples.
We present the problem description, the link and the output results
of \app. We found these anomalous values are very hard for
administrators or users to detect, because they look correct.
However, as shown in the links posted in Table~\ref{table-anomaly},
such anomalous values typically lead to critical performance
problems in practice.
